On the combination of Set Functions and Failures

### 2014-12-23 docs/src/auxiliary_files.tex
Manual extended w.r.t. hierarchical modules

The various components of \CYS create the following auxiliary files.
\begin{description}
\item[\code{prog.fcy}:] This file contains the Curry program
in the so-called ``FlatCurry'' representation where all functions are global
(i.e., lambda lifting has been performed) and pattern matching
is translated into explicit case/or expressions
(compare Appendix~\ref{sec-flatcurry}).
This representation might be useful for other back ends and
compilers for Curry and is the basis doing meta-programming in Curry.
This file is implicitly
generated when a program is compiled with \CYS.
The FlatCurry representation of a Curry program is usually
generated by the front-end after parsing, type checking and eliminating
local declarations.
If $dir$ is the directory where the Curry program is stored,
the corresponding FlatCurry program is stored in the directory
\ccode{$dir$/.curry}.

@@

\item[\code{Curry_prog.nda}:] This file contains some information about
the determinism behavior of operations that is used by the
\CYS compiler (see \cite{BrasselHanusPeemoellerReck11}
for more details about the use of this information).
If $dir$ is the directory where the Curry program is stored,
the corresponding Haskell program is stored in the directory
\ccode{$dir$/.curry/.kics2}.

\item[\code{Curry_prog.info}:] This file contains some
information about the top-level functions of module \code{prog}
that are used by the interactive environment,
like determinism behavior or IO status.
This file is stored in the same directory as \code{Curry_prog.nda}.

\item[\code{Curry_prog.hs}:] This file contains a Haskell program
as the result of translating the Curry program with the
\CYS compiler.
This file is stored in the same directory as \code{Curry_prog.nda}.

@@

>>>>

The various components of \CYS create the following auxiliary files.
\begin{description}
\item[\code{prog.fcy}:] This file contains the Curry program
in the so-called ``FlatCurry'' representation where all functions are global
(i.e., lambda lifting has been performed) and pattern matching
is translated into explicit case/or expressions
(compare Appendix~\ref{sec-flatcurry}).
This representation might be useful for other back ends and
compilers for Curry and is the basis doing meta-programming in Curry.
This file is implicitly
generated when a program is compiled with \CYS.
The FlatCurry representation of a Curry program is usually
generated by the front-end after parsing, type checking and eliminating
local declarations.

If the Curry module $M$ is stored in the directory $dir$,
the corresponding FlatCurry program is stored in the directory
\ccode{$dir$/.curry}.
This is also the case for hierarchical module names:
if the module $D1.D2.M$ is stored in the directory $dir$
(i.e., the module is actually stored in $dir/D1/D2/M.curry$),
then the corresponding FlatCurry program is stored in
\ccode{$dir$/.curry/D1/D2/M.fcy}.

@@

\item[\code{Curry_prog.hs}:] This file contains a Haskell program
as the result of translating the Curry program with the
\CYS compiler.

If the Curry module $M$ is stored in the directory $dir$,
the corresponding Haskell program is stored in the directory
\ccode{$dir$/.curry/kics2}.
This is also the case for hierarchical module names:
if the module $D1.D2.M$ is stored in the directory $dir$
(i.e., the module is actually stored in $dir/D1/D2/M.curry$),
then the corresponding Haskell program is stored in
\ccode{$dir$/.curry/kics2/D1/D2/Curry_prog.hs}.

@@

\item[\code{Curry_prog.nda}:] This file contains some information about
the determinism behavior of operations that is used by the
\CYS compiler (see \cite{BrasselHanusPeemoellerReck11}
for more details about the use of this information).
This file is stored in the same directory as \code{Curry_prog.hs}.

\item[\code{Curry_prog.info}:] This file contains some
information about the top-level functions of module \code{prog}
that are used by the interactive environment,
like determinism behavior or IO status.
This file is stored in the same directory as \code{Curry_prog.hs}.

### 2014-12-23 docs/src/overview.tex
Added missing \end{itemize} to documentation
Manual extended w.r.t. hierarchical modules

Installation instructions for \CYS can be found in
the file \code{INSTALL.txt} stored in the \CYS installation directory.
Note that there are two possibilities to install \CYS:
\begin{description}
\item[Global installation:]\index{global installation}\index{installation!global}
\CYS is installed in some global system directory where users
have no write permission. In this case, some options for experimenting
with \CYS (like \code{supply} or \code{ghc}, see below)
are not available (since they require the recompilation of parts of
the installed system).
\item[Local installation:]\index{local installation}\index{installation!local}
\CYS is installed in some local user directory where the user
has write permission and the option \code{GLOBALINSTALL}
in the \code{Makefile} of the \CYS installation is set as follows:
\begin{lstlisting}
GLOBALINSTALL=no
\end{lstlisting}
In this case, all options of \CYS are available.
\end{description}

Furthermore, \CYS can be installed with experimental support for profiling
of executables. To use profiling, two requirements have to be met:
\begin{itemize}
\item The libraries that are shipped with the GHC that is used by \CYS
have to be installed with profiling enabled. This is the default for the system
libraries contained in the GHC release, but may not be the case for additional
libraries.
\item The \code{Makefile} of \CYS contains an option \code{PROFILING}
which has to be set to \code{yes} to enable profiling support. You may
either change the Makefile to
\begin{lstlisting}
PROFILING = yes
\end{lstlisting}
or specify this setting while starting the installation process using
\begin{lstlisting}
make <optional target> PROFILING=yes
\end{lstlisting}

@@

The current implementation of \CYS supports only flat module names,
i.e., the notation \code{Dir.Mod.f} is not supported.\index{modules}
In order to allow the structuring of modules in different directories,
\CYS searches for imported modules in various directories.
By default, imported modules are searched in the directory
of the main program and the system module directories
\ccode{\cyshome/lib} and \ccode{\cyshome/lib/meta}.
This search path can be extended
by setting the environment variable \code{CURRYPATH}\pindex{CURRYPATH}
(which can be also set in a \CYS session by the option
\ccode{:set path}\pindex{path}\pindex{:set path},
see below)
to a list of directory names separated by colons (\ccode{:}).
In addition, a local standard search path
can be defined in the \ccode{.kics2rc} file
(see Section~\ref{sec-customization}).
Thus, modules to be loaded are searched in the following
directories (in this order, i.e., the first occurrence of a module file
in this search path is imported):
\begin{enumerate}
\item Current working directory (\ccode{.}) or directory prefix
of the main module (e.g., directory \ccode{/home/joe/curryprogs}
if one loads the Curry program \ccode{/home/joe/curryprogs/main}).
\item The directories enumerated in the environment variable \code{CURRYPATH}.
\item The directories enumerated in the \ccode{.kics2rc} variable
      \ccode{libraries}.
\item The directories \ccode{\cyshome/lib} and \ccode{\cyshome/lib/meta}.
\end{enumerate}
Note that the standard prelude (\code{\cyshome/lib/Prelude.curry})
will be always implicitly imported to all modules if a module
does not contain an explicit import declaration for the module
\code{Prelude}.

>>>>

Installation instructions for \CYS can be found in
the file \code{INSTALL.txt} stored in the \CYS installation directory.
Note that there are two possibilities to install \CYS:
\begin{description}
\item[Global installation:]\index{global installation}\index{installation!global}
\CYS is installed in some global system directory where users
have no write permission. In this case, some options for experimenting
with \CYS (like \code{supply} or \code{ghc}, see below)
are not available (since they require the recompilation of parts of
the installed system).
\item[Local installation:]\index{local installation}\index{installation!local}
\CYS is installed in some local user directory where the user
has write permission and the option \code{GLOBALINSTALL}
in the \code{Makefile} of the \CYS installation is set as follows:
\begin{lstlisting}
GLOBALINSTALL=no
\end{lstlisting}
In this case, all options of \CYS are available.
\end{description}
%
Furthermore, \CYS can be installed with experimental support
for profiling\index{profiling}
of executables. To use profiling, two requirements have to be met:
\begin{itemize}
\item The libraries that are shipped with the GHC that is used by \CYS
have to be installed with profiling enabled. This is the default for the system
libraries contained in the GHC release, but may not be the case for additional
libraries.
\item The \code{Makefile} of \CYS contains an option \code{PROFILING}
which has to be set to \code{yes} to enable profiling support. You may
either change the Makefile to
\begin{lstlisting}
PROFILING = yes
\end{lstlisting}
or specify this setting while starting the installation process using
\begin{lstlisting}
make <optional target> PROFILING=yes
\end{lstlisting}
\end{itemize}

@@

\CYS searches for imported modules in various directories.
By default, imported modules are searched in the directory
of the main program and the system module directories
\ccode{\cyshome/lib} and \ccode{\cyshome/lib/meta}.
This search path can be extended
by setting the environment variable \code{CURRYPATH}\pindex{CURRYPATH}
(which can be also set in a \CYS session by the option
\ccode{:set path}\pindex{path}\pindex{:set path},
see below)
to a list of directory names separated by colons (\ccode{:}).
In addition, a local standard search path
can be defined in the \ccode{.kics2rc} file
(see Section~\ref{sec-customization}).
Thus, modules to be loaded are searched in the following
directories (in this order, i.e., the first occurrence of a module file
in this search path is imported):
\begin{enumerate}
\item Current working directory (\ccode{.}) or directory prefix
of the main module (e.g., directory \ccode{/home/joe/curryprogs}
if one loads the Curry program \ccode{/home/joe/curryprogs/main}).
\item The directories enumerated in the environment variable \code{CURRYPATH}.
\item The directories enumerated in the \ccode{.kics2rc} variable
      \ccode{libraries}.
\item The directories \ccode{\cyshome/lib} and \ccode{\cyshome/lib/meta}.
\end{enumerate}
The same strategy also applies to modules with a hierarchical
module name with the only difference that the hierarchy prefix
of a module name corresponds to a directory prefix of the module.
For instance, if the main module is stored in directory \code{MAINDIR}
and imports the module \code{Test.Func}, then the module stored in
\code{MAINDIR/Test/Func.curry} is imported (without setting
any additional import path) according to the
module search strategy described above.

Note that the standard prelude (\code{\cyshome/lib/Prelude.curry})
will be always implicitly imported to all modules if a module
does not contain an explicit import declaration for the module
\code{Prelude}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "manual"
%%% End:
